Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-13 ms.tex
Updates from Overleaf

  \item 
    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
    third column respectively in Figure~\ref{fig:results}) can lead
    social learning to be selected for even for large values of $u$, possibly
    due to the low risk and potentially high reward of learning an accurate
    tally of mean payoffs from the previous generation. 
    Since there are so many behaviors and so
    few observations, softmax weighting will not significantly 
    favor a sub-optimal behavior. However, if one does learn an accurate tally
    then one does have an increased chance of performing the best one.
    \begin{itemize}
      \item 
        (THIS MAKES SENSE, BUT THE EFFECT IS TOO STRONG. WHY SHOULD THERE BE ANY
        SOCIAL LEARNING WHEN U = 1.0?  I THINK SOMETHING IS SLIGHTLY WRONG WITH THE
        MODEL---I'M WORKING ON CHECKING WHAT THAT MIGHT BE)
      \item
        ONE THING TO CHECK IS THE FRACTION DOING THE OPTIMAL BEHAVIOR WHEN
        $u=1$. IF MANY START OUT DOING OPTIMAL, THEN SOMETHING MAY BE WRONG.
    \end{itemize}

@@

\bibliography{/Users/mt/workspace/Writing/library.bib}
% \bibliography{this.bib}

>>>>

  \item 
    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
    third column respectively in Figure~\ref{fig:results}) can lead
    social learning to be selected for even for large values of $u$, possibly
    due to the low risk and potentially high reward of learning an accurate
    tally of mean payoffs from the previous generation. 
    Since there are many behaviors and
    few observations, softmax weighting will not significantly 
    favor a sub-optimal behavior. However, if one does learn an accurate tally
    then one does have an increased chance of performing the best one.
    \begin{itemize}
      \item 
        (THIS MAKES SENSE, BUT THE EFFECT IS TOO STRONG. WHY SHOULD THERE BE ANY
        SOCIAL LEARNING WHEN U = 1.0?  I THINK SOMETHING IS SLIGHTLY WRONG WITH THE
        MODEL---I'M WORKING ON CHECKING WHAT THAT MIGHT BE)
      \item
        ONE THING TO CHECK IS THE FRACTION DOING THE OPTIMAL BEHAVIOR WHEN
        $u=1$. IF MANY START OUT DOING OPTIMAL, THEN SOMETHING MAY BE WRONG.
    \end{itemize}

@@

% \bibliography{/Users/mt/workspace/Writing/library.bib}
\bibliography{this.bib}
